Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-20 paper.tex
Don't use empty page style for first page
Use report instead of article
Use adapted suthesis-2e.sty
Replaced sections with chapters
Replaced subsections with sections
Revised abstract for new results

\documentclass{article}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{fancyvrb}
\usepackage{pgfplots}

@@

% Use an empty page style for the title and abstract
\pagestyle{empty}

% =====
% Title
% =====
\title{Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations}
\author{Andrew Brown \and Joe Geigel}
\date{\small{Rochester Institute of Technology}}
\maketitle

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Methods for rendering an arbitrary number of intersecting volumes using hardware
acceleration have been developed, but they generally require a large amount of
geometry to be created every frame.  In the simple case where two axis-aligned
volumes intersect, it is shown that Boolean operations can be used so that
the camera may move without regenerating any geometry.  However, the two
variations presented herein still achieve similar frame rates to that of the
canonical slicing method.
\end{abstract}

@@

% ============
% Introduction
% ============
\section{Introduction}

@@

% ==========
% Background
% ==========
\section{Background}

@@

% =============
% Previous Work
% =============
\section{Previous Work}

\subsection{Overview}

@@

\subsection{Slicing}

@@

\section{Ray Casting}

@@

% ==========
% Approaches
% ==========
\section{Approaches}

@@

\subsection{Boolean AND with Depth Buffer Masking}

@@

\subsection{Boolean AND with Boolean XOR}

@@

% ==============
% Implementation
% ==============
\section{Implementation}

@@

% ==========
% Evaluation
% ==========
\section{Evaluation}

>>>>

\documentclass{report}
\usepackage{suthesis-2e}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{fancyvrb}
\usepackage{pgfplots}

@@

% =====
% Title
% =====
\title{Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations}
\author{Andrew Brown}
\dept{Computer Science}
\committeechair{Professor Joe Geigel, Ph.D.}
\reader{Professor Reynold Bailey, Ph.D.}
\observer{Professor Warren Carithers}
\grantdate{June}{2013}

\beforepreface
\afterpreface

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Methods for rendering an arbitrary number of intersecting volumes using hardware
acceleration have been developed, but they generally require a large amount of
geometry to be created every frame.  In the simple case where two axis-aligned
volumes intersect, it is shown that Boolean operations can be used so that
the camera may move without regenerating any geometry.  Furthermore, samples
that do not contribute to the final image may be completely avoided.  The two
variations presented herin achieve higher frame rates than the traditional
slicing method.
\end{abstract}

@@

% ============
% Introduction
% ============
\chapter{Introduction}

@@

% ==========
% Background
% ==========
\chapter{Background}

@@

% =============
% Previous Work
% =============
\chapter{Previous Work}

\section{Overview}

@@

\section{Slicing}

@@

\chapter{Ray Casting}

@@

% ==========
% Approaches
% ==========
\chapter{Approaches}

@@

\section{Boolean AND with Depth Buffer Masking}

@@

\section{Boolean AND with Boolean XOR}

@@

% ==============
% Implementation
% ==============
\chapter{Implementation}

@@

% ==========
% Evaluation
% ==========
\chapter{Evaluation}
